%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Malik Wensman} \\ \vspace{1pt}
    \small 763-313-0935 $|$ \href{mailto:malikadidw@gmail.com}{\underline{malikadidw@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/malik-diallo-wensman-989041260/}{\underline{linkedin.com/in/malik-diallo-wensman-989041260/}} $|$
    \href{https://github.com/mdw223}{\underline{github.com/mdw223}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NC State University}{Raleigh, NC}
      {Bachelor Degree in Computer Science}{Aug. 2022 -- Present}
      \resumeItem{Year: Junior. Expected Graduation: May 2026. GPA: 3.71. On the Dean's List Of Achievement.}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Engineering Intern}{05/2023 - 07/2023}
      {NC Soil and Water Conservation Division}{Raleigh, NC}
      \resumeItemListStart
        \resumeItem{Mapped watersheds using GIS software like ArcMap}
        \resumeItem{Calculated water runoff in various terrains and land uses, utilizing EFH-2 for flood prevention and soil conservation efforts}
        \resumeItem{Collaborated on the design and evaluation of ponds for agricultural or conservation purposes, using WinPond and Civil 3D}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading 
      {Math Tutor}{Sep 2022 – July 2024}
      {Mathnasium}{Garner, NC}
      \resumeItemListStart
        \resumeItem{Managed and taught up to 3 students at a time, personalizing instruction to meet individual learning needs for diverse age groups from Pre-K to college.}
        \resumeItem{Fostered an engaging and supportive environment, motivating students to develop a positive attitude toward math and a growth mindset.}
    \resumeItemListEnd
    \textbf{Other work experience}{: Dickison Low Voltage (Electrical Wiring
Assistant), Grade Potential Tutoring (Math and French Tutor), Blaze Pizza, Walgreens}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{PackHealth (EHR) software} $|$ \emph{Java, Data Structures, Algorithms}}{10/2024 - 11/2024}
          \resumeItemListStart
            \resumeItem{Developed a secure user activity logging system that complies with new cybersecurity standards,}
            \resumeItem{designed algorithms and implemented data structures.}
            \resumeItem{Conducted performance analysis and tested to ensure efficiency.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{FEDD DAY 2023 Entrepreneurship Competition} $|$ \emph{Solidworks, 3D Printing, Presentation}}{01/2023 - 05/2023}
          \resumeItemListStart
            \resumeItem{Team Won the FEDD DAY 2023 Entrepreneurship Competition, designed a Device Holder using SolidWorks and 3D Printing}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C++, SQL, HTML} \\
     \textbf{Knowledge/Skills}{: Testing/Debugging, Object-Oriented Design, Performance Analysis, Data Structures, Algorithms, Data Science, Database Management} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}
 
%-----------Clubs-----------
\section{Club Engagement}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{ColorStack}{: As an active member of ColorStack, I engage in initiatives supporting Black and Latinx students in technology by networking, participating in professional development, collaborating on technical projects, and advocating for diversity and inclusion.} \\
     \textbf{NSBE (National Society of Black Engineers)}{: As an active NSBE member, I engage in workshops, networking, and projects to empower Black engineers, promote diversity in STEM, and support academic excellence, career readiness, and community outreach.}
    }}
 \end{itemize}
 


%-------------------------------------------
\end{document}
